TGI Spinal Analysis Code

### 2022-12-05 analysis/tgi-spinal_analysis.Rmd
calculating difference across cnt and tgi for h1

ggplot(data = vas_h1, aes(colour = condition, group = ID)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'CNT', condition == 'within'),
               aes(xj, VAS), position = position_nudge(-.1)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'CNT', condition == 'across'),
               aes(xj, VAS), position = position_nudge(.1)) +
  scale_colour_manual(values = c(purp[6], purp[3])) +
  scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
  theme_classic() -> h1_cnt_plot

ggplot(data = vas_h1, aes(colour = condition)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'TGI', condition == 'within'),
               aes(xj, VAS), position = position_nudge(-.1)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'TGI', condition == 'across'),
               aes(xj, VAS), position = position_nudge(.1)) +
  scale_colour_manual(values = c(purp[6], purp[3])) +
  scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
  theme_classic() -> h1_tgi_plot

h1_plot <- ggarrange(h1_cnt_plot, h1_tgi_plot,
                     ncol = 2, nrow = 1,
                     common.legend = TRUE)
h1_plot
```

>>>>

ggplot(data = vas_h1, aes(colour = condition, group = ID)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'CNT', condition == 'within'),
               aes(xj, VAS), position = position_nudge(-.1)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'CNT', condition == 'across'),
               aes(xj, VAS), position = position_nudge(.1)) +
  scale_colour_manual(values = c(blue[6], blue[3])) +
  scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
  labs(title = 'Non TGI', y = 'Visual Analogue Scale 0 - 100', 
       x = 'Sensation') +
  theme_classic() -> h1_cnt_plot

ggplot(data = vas_h1, aes(colour = condition)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'TGI', condition == 'within'),
               aes(xj, VAS), position = position_nudge(-.1)) +
  geom_point(data = vas_h1 %>% 
               filter(manipulation == 'TGI', condition == 'across'),
               aes(xj, VAS), position = position_nudge(.1)) +
  scale_colour_manual(values = c(purp[6], purp[3])) +
  scale_x_continuous(breaks=c(1,2,3), labels=c("cold", "warm", "burn")) +
  labs(title = 'TGI', y = NULL, 
       x = 'Sensation') +
  theme_classic() -> h1_tgi_plot

h1_plot <- ggarrange(h1_cnt_plot, h1_tgi_plot,
                     ncol = 2, nrow = 1,
                     common.legend = TRUE)
h1_plot

# difference between across and within 
# first remove jitter
vas_h1 <- vas_h1[, c(1:7)]
# then pivot wider and calculate difference
vas_h1_diff <- vas_h1 %>% 
  pivot_wider(names_from = manipulation, values_from = VAS) %>% 
  mutate(difference = TGI - CNT)

# now plot the difference
```
